### 2016-12-06 README.Rmd
... now refers to stats::predict arguments

In this example, we fit a random forest to the Boston housing data. (See `?boston` for a brief explanation of the data.) Note, for any of the following examples, you can see a progress bar by simply specifying `.progress = "text"` in the call to `partial`. You may also reduce the computation time via the `grid.resolution` option in the call to `partial`.
```{r, message = FALSE, warning=FALSE, fig.show="hold"}
# Load required packages
library(pdp)  # for constructing PDPs
library(randomForest)  # for random forest algorithm

@@

# Partial dependence of lstat and rm on cmedv
partial(boston.rf, pred.var = "lstat", plot = TRUE, rug = TRUE)
partial(boston.rf, pred.var = "age", plot = TRUE, rug = TRUE)
partial(boston.rf, pred.var = c("lstat", "rm"), plot = TRUE, chull = TRUE)
```

>>>>

In this example, we fit a random forest to the Boston housing data. (See `?boston` for a brief explanation of the data.) Note, for any of the following examples, you can see a progress bar by simply specifying `progress = "text"` in the call to `partial`. You may also reduce the computation time via the `grid.resolution` option in the call to `partial`.
```{r, message = FALSE, warning=FALSE, fig.show="hold"}
# Load required packages
library(pdp)  # for constructing PDPs
library(randomForest)  # for random forest algorithm

@@

# Partial dependence of lstat and rm on cmedv
partial(boston.rf, pred.var = "lstat", plot = TRUE, rug = TRUE)
partial(boston.rf, pred.var = "rm", plot = TRUE, rug = TRUE)
partial(boston.rf, pred.var = c("lstat", "rm"), plot = TRUE, chull = TRUE)
```
